---
title: "Stat131A lecture 27"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE,echo=TRUE}
library(DataComputing)

```

##`replicate() in R`

`replicate()` repeats a function over and over again.
For example suppose you have a function that returns the phrase "I Love Stats". Replicate print this out many times. It is generally faster than using a traditional loop.

```{r}
B=5
fun <- function(){
  return("I love Stats!")
}
fun()

my_vec <- replicate(B,fun())
my_vec
```

Here is another example for you to try:

###Lets make a deal

What is better deal?


Win $1 if out of 10 flips of fair coin you get exactly 5 heads.


Win $1 if out of 100 flips of fair coin you get exactly 50 heads.

We are going to make a simulation of flipping a coin `size=100` number times and seeing if we get exactly 50. We will do this exeriment `B=200` times and compute the percentage of times that it is exactly 50.




```{r norm3, exercise=TRUE, exercise.eval=FALSE}

B=200

fun <- function(size){
  vec <- sample(c(0,1),size = size,prob=c(.5,.5),replace = TRUE)
  sum(vec)==(.5)*size
}

#add replicate command here. Assign the name my_vec to the output of replicate.



```




```{r norm3-solution}

B=200

fun <- function(size){
  vec <- sample(c(0,1),size = size,prob=c(.5,.5),replace = TRUE)
  sum(vec)==(.5)*size
}

my_vec <- replicate(B, fun(100))
my_vec
mean(my_vec)

```

The answer is the expected number of dollars you will win playing the game B=100 times.
if you put in 10 for size you get bigger number than if you put 100 in for size so you should take the first deal.


##Central Limit Theorem

Lets make a box:
```{r}
a <- rep(0,each=7)  
b <- rep(1,each=3)  #box is 30% 1 and 70% 0
box <- c(a,b)  #this is your box
box
mean(box)

```

Lets make a function that draws a sample of size 100 from the box with replacement and takes the sum of your sample.

```{r}
sample_size <- 100
fun <- function(){
  my_sample <- sample(box,size=sample_size,replace=TRUE)
  sum(my_sample)
}  
fun()


```

Lets call this function many times and make a histogram of all of the sums.

```{r}
B=1000
sum_sample <- replicate(B,fun())
head(sum_sample, 50)
df <- data.frame(sum_sample)
head(df)
df %>% ggplot(aes(x=sum_sample,y=..density..)) + geom_histogram(bins=10)
```



```{r,norm1-setup, exercise = FALSE, exercise.setup = "exper-hist2", exercise.eval = FALSE, message=FALSE}
library(DataComputing)

```

What happens to the histogram if you make the box more loopside by making it 99% 0 and 1% 1. What happens now if you make `sample_size` large. Experiment...

```{r exper-hist2, exercise=TRUE, exercise.eval=FALSE,message=FALSE}
library(DataComputing)
sample_size <- 100    #change this
a <- rep(0,each=2)   #change this
b <- rep(1,each=1)   
box <- c(a,b)
box

fun <- function(){
  my_sample <- sample(box,size=sample_size,replace=TRUE)
  sum(my_sample)
}  
B <- 1000
sum_sample <- replicate(B,fun())
df <- data.frame(sum_sample)
df %>% ggplot(aes(x=sum_sample,y=..density..)) + geom_histogram(bins=10)
```

```{r exper-hist2-hint}
# if you make the box more loop sided you need a larger sample size to get a normal distribution for the sum
```




