---
title: "Stat131 lecture 6"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE,echo=TRUE}
library(dplyr)
library(ggplot2)

```


This solves problem 1 page 93 in FPP using R.

## part a


```{r}
data <- c(39,41,47,58,65,37,37,49,56,59,62,36,48,52,64,29,44,47,49,52,53,54,72,50,50)
```


```{r,norm-setup, exercise = FALSE, exercise.setup = "norm", exercise.eval = FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
data <- c(39,41,47,58,65,37,37,49,56,59,62,36,48,52,64,29,44,47,49,52,53,54,72,50,50)
```


Find the mean and standard deviation of the data using the functions `mean()` and `sd()`. Assign these numbers the name `avg` and `std`

```{r norm, exercise=TRUE, exercise.eval=FALSE, message=FALSE}


```


```{r norm-solution}
avg <- mean(data)
avg
std <- sd(data)
std
```


Lets check that this data is approximately normal by making a histogram.  You will learn to plot with ggplot() very soon. 
```{r, echo=FALSE}
df <- data.frame(data)
df %>% ggplot() + geom_histogram(aes(x=data, y=..density..), binwidth=10)
```

Find the numbers `avg-1.25*std` and `avg+1.25*std`. Assign these numbers the name `low` and `high`.


```{r,norm1-setup, exercise = FALSE, exercise.setup = "norm", exercise.eval = FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
data <- c(39,41,47,58,65,37,37,49,56,59,62,36,48,52,64,29,44,47,49,52,53,54,72,50,50)
avg <- mean(data)
std <- sd(data)
low <- avg-1.25*std
high <- avg+1.25*std
```


```{r norm1, exercise=TRUE, exercise.eval=FALSE, message=FALSE}


```


```{r norm1-solution}
low <- avg-1.25*std
low
high <- avg+1.25*std
high
```


Assuming the data is normally distributed find the area between `low` and `high`.

```{r,norm2-setup, exercise = FALSE, exercise.setup = "norm", exercise.eval = FALSE, message=FALSE}
library(dplyr)
library(ggplot2)
data <- c(39,41,47,58,65,37,37,49,56,59,62,36,48,52,64,29,44,47,49,52,53,54,72,50,50)
avg <- mean(data)
std <- sd(data)
low <- avg-1.25*std
high <- avg+1.25*std
```



```{r norm2, exercise=TRUE, exercise.eval=FALSE, message=FALSE}
#modify the following
pnorm(__fill_in__)- pnorm(__fill_in__)
```


```{r norm2-solution}
pnorm ((high-avg)/std) - pnorm((low-avg)/std)
```


So we expect 78.87 percent of the data to be within 1.25 SD of the mean.
We can write the following expression to find how many scores we are expecting:

```{r}
.7887*length(data)  #the proportion of values between low and high times the total number of scores.
```


##part b


We can count how many scores between `low` and `high` using vector subsetting.

```{r,norm3-setup, exercise = FALSE, exercise.setup = "norm", exercise.eval = FALSE, message=FALSE,echo=FALSE}
library(dplyr)
library(ggplot2)
data <- c(39,41,47,58,65,37,37,49,56,59,62,36,48,52,64,29,44,47,49,52,53,54,72,50,50)
avg <- mean(data)
std <- sd(data)
low <- avg-1.25*std
high <- avg+1.25*std
```

Find the values of data between low and high. Then have R count these values using the function `length()`.
```{r, norm3, exercise=TRUE, exercise.eval=TRUE,message=FALSE}


```




```{r norm3-solution}
data[data>low & data<high] #values of data between low and high
length(data[data>low & data<high]) #the number of scores between low and high
```

18 values are between low and high. Pretty close to 19.71.

