---
title: "Stat131A lecture 36"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE,echo=TRUE}
library(DataComputing)
```


#Example of bootstrapping a 95% CI  

### Data Cleaning a data set.
Lets load some maternity data from the Kaiser database into R.

```{r message=FALSE}

#the function load, loads a dataset into your workspace. It outputs a vector of all dataframes in the data set. In this case there is just one data set called infants. 
data <- load(url("https://www.stat.berkeley.edu/users/nolan/data/KaiserBabies.rda"))
data

 #We will eliminate observations if the `smoke` doesn't take the value `smoke=Never` or `smoke=Now`. 

infants <- infants %>% filter(smoke=="Never" |  smoke =="Now") 
infants <- na.omit(infants)  #remove all NA from data frame
```


```{r}
head(infants)
```

This data set contains a sample of personal information about the family of babies born at Kaiser in San Francisco. We wish to get a 95% CI for the population weight of the San Francisco mothers at the time of delivery. We will use variable `wt`.


### Step 1: Take a sample one time from your population.

This was already done by Kaiser in creating the data set. The sampling method isn't important to us although we assume that it is unbiased.

```{r}
mysample <- infants$wt
sample_size <- length(mysample)
sample_mean <- mean(mysample)  # the mean of your original sample
sample_size
sample_mean
```

### Step 2: Resample from `mysample` B=1000 times with replacement (size `sample_size`). Form a vector of sample estimates of your parameter.


```{r}

B=1000
# the function is used to find the average of each size-100 samples
find_avg <- function(){
  resample <- sample(mysample, size = 570, replace = T)
  xbar <- mean(resample)
  xbar
}
# we will run the above function 1000 times
vec <- replicate(B, find_avg())
```

### Step 3: subtract your `sample_mean` from your vector of estimates


```{r}
vec_minus_mean <- vec - sample_mean
```

### Step 4: Find the 2.5th and 97.5th percentile of your vector

```{r}
a <- quantile(vec_minus_mean, .025)
b <- quantile(vec_minus_mean, .975)
a
b
```

### Step 5: Find the 95% CI

```{r}
bootCI <- c(sample_mean-b,sample_mean-a)
bootCI
```



###Your turn:

Find a 90% CI for the median gestation period `gestation` from the  `infants` data set above.

```{r,exper-his2-setup, exercise = FALSE, exercise.setup = "exper-hist", exercise.eval = FALSE, message=FALSE}
library(dplyr)
library(ggplot2)

data <- load(url("https://www.stat.berkeley.edu/users/nolan/data/KaiserBabies.rda"))
data
infants <- na.omit(infants) 

set.seed(7)   #The function set.seed makes it so that everyone will be using the same sample.

infants <- infants %>% filter(smoke=="Never" |  smoke =="Now") 
infants <- na.omit(infants)  #remove all NA from data frame

```


```{r exper-his2, exercise=TRUE, exercise.eval=FALSE}

```


```{r exper-his2-solution}

mysample =infants$gestation
sample_size <- length(mysample)
sample_med <- median(mysample)  # the mean of your original sample
sample_size
sample_med

B=1000
# the function is used to find the average of each size-100 samples
find_median <- function(){
  resample <- sample(mysample, size = 570, replace = T)
  med <- median(resample)
  med
}

# we will run the above function 1000 times
vec <- replicate(B, find_median())
vec_minus_med <- vec - sample_med

a <- quantile(vec_minus_med, .05)
b <- quantile(vec_minus_med, .95)
a
b

bootCI <- c(sample_med-b,sample_med-a)
bootCI
```


