---
title: "Stat131A lecture 28"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE,echo=TRUE}
library(DataComputing)

```

##SE of the percentage simulation

```{r,norm1-setup, exercise = FALSE, exercise.setup = "exper-hist2", exercise.eval = FALSE, message=FALSE}
library(DataComputing)

```
The population of New Mexico is 1M with 50% democrats and we are taking a sample size of 10,000. We wish to know what is a more accurate assesment of the true % of democrats in NM, to randomly sample with or without replacement. To answer this question you will compute the SE of the percentage of democrats with and without replacement.

To make the simulation run faster lets scale down the population of your box and sample size by a factor or 1000 (i.e. pop size is 1,000, and sample size is 10).

Here is a sample of size 10 of our box drawn without replacement:
```{r}
pop <- 1000
sample_size <- 10  
a <- rep(0,each=pop/2)  #Republican 
b <- rep(1,each=pop/2)  #Democrat
box <- c(a,b)
my_sample <- sample(box,size=sample_size,replace=FALSE)
my_sample
```

Write a function called `fun` that takes no input and creates a sample of 1 and 0 from the box without replacement and outputs the percentage of 1 in your sample.

```{r exper-hist1, exercise=TRUE, exercise.eval=FALSE,message=FALSE}
pop <- 1000
sample_size <- 10  
a <- rep(0,each=pop/2)  #Republican
b <- rep(1,each=pop/2)  #Democrat
box <- c(a,b)

#__fill_in__

fun()
```

```{r exper-hist1-solution}
pop <- 1000
sample_size <- 10   
a <- rep(0,each=pop/2)   
b <- rep(1,each=pop/2)   
box <- c(a,b)

fun <- function(){
  my_sample <- sample(box,size=sample_size,replace=boolean)
  mean(my_sample)*100
}  
fun()
```

Next replicate `fun` to create a vector of sample percentages.  Take the SD of all of the sample percentages to find the SE of the percentage of democrats with and without replacement. Here is a template of what you need. 

```{r exper-hist2, exercise=TRUE, exercise.eval=FALSE,message=FALSE}
pop <- 1000
sample_size <- 10  
a <- rep(0,each=pop/2)  #Republican
b <- rep(1,each=pop/2)  #Democrat
box <- c(a,b)

for(boolean in c(TRUE,FALSE)){
fun <- function(){
  my_sample <- sample(box,size=sample_size,replace=boolean)
  __fill_in__
}  
B <- 1000
vec_percentages <- replicate(B,fun())
print(__fill_in__)
}
```

```{r exper-hist2-solution}
pop <- 1000
sample_size <- 10   
a <- rep(0,each=pop/2)   
b <- rep(1,each=pop/2)   
box <- c(a,b)
for(boolean in c(TRUE,FALSE)){
  fun <- function(){
    my_sample <- sample(box,size=sample_size,replace=boolean)
    mean(my_sample)*100
  }  
 B <- 1000
  vec_percentages <- replicate(B,fun())
  print(sd(vec_percentages))
}

```



