---
title: "Stat131A lecture 24"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```

```{r, message=FALSE,echo=TRUE}
library(DataComputing)

```



##`sample()` in R

You can simulate playing Nevada Roulette 10 times using the R function `sample()`

```{r}
vec <- sample(c("b","r","g"),size=10,prob=c(18/28,18/38,2/38),replace=TRUE)
vec
```

You count the number of "r" in the sample vector (i.e. the number of red pockets you landed on in 10 games)

```{r}
vec=="r"   #this is a boolean vector
sum(vec=="r")
sum(vec=="r")/length(vec)
```

```{r,norm11-setup, exercise = FALSE, exercise.setup = "norm", exercise.eval = FALSE, message=FALSE}
library(DataComputing)

```

Use the function `sample()` to simulate rolling a fair die 60 times. Also compute the fraction of 1 that you get.

```{r norm11, exercise=TRUE, exercise.eval=FALSE}

```



```{r norm11-solution}
vec <- sample(c(1,2,3,4,5,6),size=60,prob=c(1/6,1/6,1/6,1/6,1/6,1/6),replace=TRUE)
vec
sum(vec==1)/length(vec)
```


##`for()` loop and `data.frame()` in R

Lets find the number of heads in both 10 and 100 coin tosses. Here is a way to do it using a `for()` loop.
```{r}
num_heads_vec=c()
for(size in c(10,100)){
  vec <- sample(c("head","tail"),size=size,prob=c(1/2,1/2),replace=TRUE)
  num_heads_vec <- c(num_heads_vec,sum(vec=="head"))
}
num_heads_vec
```

Suppose you have vectors 
```{r}
a <- c(1,2,3)
b <- c("a","b","c")
```
You can make a data frame with column variables `a` and `b` using the function `data.frame()`
```{r}
data.frame(a,b)
```




```{r,norm-setup, exercise = FALSE, exercise.setup = "norm", exercise.eval = FALSE, message=FALSE}
library(DataComputing)

```

Copy the code above into the console and modify it so that you create a data frame with column variables equal to the number of coin tosses and the number of heads you get for different number of coin tosses.


```{r norm, exercise=TRUE, exercise.eval=FALSE}


```



```{r norm-solution}
size_vec=c()
num_heads_vec=c()
for(size in c(10,100)){
  vec <- sample(c("head","tail"),size=size,prob=c(1/2,1/2),replace=TRUE)
  size_vec=c(size_vec,size)
  num_heads_vec <- c(num_heads_vec,sum(vec=="head"))
}
df <- data.frame(size_vec,num_heads_vec)
df
```


##Law of Averages

Consider flipping a fair coin a certain number of times. Here is a graph of the percentage of heads that you get. This result is the the Law of Averages.

```{r}
size_vec=c()
num_heads_vec=c()
for (size in c(100, 1000, 10000, 100000, 1000000, 10000000)){
  vec <- sample(c("head","tail"),size=size,prob=c(1/2,1/2),replace=TRUE)
  size_vec=c(size_vec,size)
  num_heads_vec <- c(num_heads_vec,sum(vec=="head"))
}
df <- data.frame(log_size=log(size_vec,base=10),num_heads=num_heads_vec, error=num_heads_vec - size_vec*.5, percent_heads= 100*num_heads_vec/size_vec, percent_error=100*(num_heads_vec - size_vec*.5)/size_vec)
df
 
df %>% ggplot(aes(x=log_size, y=percent_heads)) + geom_line() + geom_hline(yintercept=50, col="red")
```


Law of Averages: The % heads converges to the expected number of heads (i.e. the % chance error goes to zero) as the number of coin tosses goes to infinity.


```
```{r}
library(mosaicData)

plot_it <- function(flag){
  if(flag=="yes"){
    my_plot<- CPS85 %>% ggplot(aes(x=exper,wage)) + geom_point(aes(color=sex, shape=sex))
    print(my_plot)
  }
}
plot_it("no")
```


