---
title: "Stat131A lecture 12"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```


##Practice with functions problem 1

Recall this is how you tested that a year is a leap year:
```{r,eval=FALSE}
year <-  2013
if((year%%4==0 & year%%100 != 0) | (year%% 400 ==0)  ) leapyear <- TRUE  else leapyear <- FALSE
leapyear
```


Make a function called `test_year` that inputs a year and outputs whether the year is a leap year. Call the function with the year 2000 to see whether 2000 was a leap year.


```{r,cond, exercise = TRUE, exercise.setup = "cond-setup", exercise.eval = FALSE, message=FALSE}

```

```{r  cond-hint, echo = FALSE}

# test_year <- function(year){
#etc ...
#}
# test_year(2000)

```



```{r cond-solution, echo = FALSE}
test_year <- function(year){
  if((year%%4==0 & year%%100 != 0) | (year%% 400 ==0)) {
    leapyear <- TRUE}
  else {
    leapyear <- FALSE}  
  leapyear
}
test_year(2000)
```


```{r,include=TRUE}

```

##Practice with functions problem 2

Recall that this is how we simulated rolling a die until you get a 4 creating a vector of 

```{r,eval=FALSE}
myrolls <- c()
roll <- 1000 #some number not 1 through 6
while(roll != 4){
  roll <- sample(1:6,1)
  myrolls <- c(myrolls,roll)
}
myrolls
```

Write a function called `coin_toss` that inputs a positive integer, n, and outputs a random vector of tails and heads (1 and 0) until you get your nth head. Call the function with n=3 and examine the vector output to make sure it makes sense.


```{r,loop, exercise = TRUE, exercise.setup = "DC-2017-02-14-08371a-setup", exercise.eval = FALSE}

```

```{r  loop-hint, echo = FALSE}
#coin_toss <- function(n){
#  etc...
#}  
#coin_toss(3)

```



```{r loop-solution, echo = FALSE}
coin_toss <- function(n){
  mytosses <- c()
  counter <- 0
  while(counter<n){
    toss <- sample(0:1,1)
    mytosses <- c(mytosses,toss)
    if(toss==1){
      counter=counter+1
    }
  }
  mytosses
}
coin_toss(3)
```


##Practice with functions problem 3

Write a function that approximates the value of pi by summing the terms of this series:
4/1-4/3+4/5-4/7+4/9-4/11+ ...  The function has a single input, n, which is the number of terms to sum. It outputs the sum of the first n terms of this series, as well as the difference of the sum and pi. Call the function to estimate pi with 20 terms.



```{r,loop3, exercise = TRUE, exercise.setup = "DC-2017-02-14-0837a-setup", exercise.eval = FALSE}

```

```{r  loop3-hint, echo = FALSE}
#use a for loop
#sum=0
#for(i in 1:n){
 #   increment <- (-1)^(i+1) * 4/(2*i-1)
#    sum=sum + increment

#to return multiple values use a list  (i.e. return(list(sum, pi-sum))

```



```{r loop3-solution, echo = FALSE}
my_pi <- function(n){
  sum=0
  for(i in 1:n){
    increment <- (-1)^(i+1) * 4/(2*i-1)
    sum=sum + increment
  }
  return(list(sum, pi-sum))
}
my_pi(20)
```


```



