---
title: "Stat131 lecture 9"
output: learnr::tutorial
runtime: shiny_prerendered
---

```{r setup, include=FALSE}
library(learnr)
knitr::opts_chunk$set(echo = TRUE)
```


##Practice with conditionals 
The basic syntax for an `if/else` statement is

```{r, eval=FALSE}
if ( condition ) {
  statement1
} else {
  statement2
}
```

You can also write this on a single line as:
```{r, eval=FALSE}
if(condition) statement1 else statement2
```

In the exercise below you will determine whether the year 2013 is a leap year. The condition for a year to be a leap year is written in terms of the modulo operator, `%%` in R. 

For example
```{r}
15 %% 2
15 %% 3
```

We see that 15 modulo 2 is one because the remainder when you divide 15 by 2 is 1. Similarly when you divide 15 by 3 you don't get any remainder.


Assign **TRUE** to the boolean variable leapYear if the integer variable year is a
leap year and **FALSE** otherwise. The rule for determining leap years is that one of the following conditions must hold:
1) the year is divisible by 4 but not divisible by 100, or 
2) the year is divisible by 400.

Below you will figure out if the year 2013 is a leap year.
```{r,cond, exercise = TRUE, exercise.setup = "cond-setup", exercise.eval = FALSE, message=FALSE}
year <- 2013
if( __fill_in__  ) {leapyear <- __fill_in__
}else{
  leapyear <- __fill_in__
}
leapyear
```

```{r  cond-hint, echo = FALSE}

# if((year%%4==0 & year%%100 != 0) | (year%% 400 ==0)  ) leapyear <- TRUE 
# etc....

```



```{r cond-solution, echo = FALSE}
year <-  2013
if((year%%4==0 & year%%100 != 0) | (year%% 400 ==0)  ) leapyear <- TRUE  else leapyear <- FALSE
leapyear
```


```{r,include=TRUE}

```

##Practice with loops

Recall the syntax or `for` and `while` loops:

```{r, eval=FALSE}

for ( name in vector ){
  statement
}

```


```{r,eval=FALSE}
while (condition){
  statement
}
```


Simulate rolling a die until you get a 4. Create a vector of your rolls.


```{r,loop, exercise = TRUE, exercise.setup = "DC-2017-02-14-08371a-setup", exercise.eval = FALSE}
myrolls <- c()
roll <- 1000 #some number not 1 through 6
while(roll != 4){
  roll <- __fill_in__
  myrolls=c(myrolls,roll)
}
myrolls
```

```{r  loop-hint, echo = FALSE}

# sample(1;2,1) is a coin toss.Adpat this to roll a die.

```



```{r loop-solution, echo = FALSE}
myrolls <- c()
roll <- 1000 #some number not 1 through 6
while(roll != 4){
  roll <- sample(1:6,1)
  myrolls=c(myrolls,roll)
}
myrolls
```


The `break` statement causes a loop to exit. You will see an example in the next question.

Here is a character vector called `chars`

```{r loop1-setup, echo = FALSE}
# Pre-defined variables
rquote <- "R's internals are irrefutably intriguing"
chars <- strsplit(rquote, split = "")[[1]]
```

```{r, echo=FALSE}
rquote <- "R's internals are irrefutably intriguing"
chars <- strsplit(rquote, split = "")[[1]]
chars
```



Count the number of "r"s (both "r" and "R") that come before the first letter "u"  (both "u" and "U") in the rquote character string. Store the result in a variable rcount.



```{r loop1, exercise = TRUE,  exercise.eval = FALSE, exercise.setup = "loop1-setup"}

rcount <- 0
for (char in chars) {
  if (char == "u" | char == "U") {
    break
  }
  __fill_in__
}

# Print the resulting rcount variable to the console
rcount




```

```{r  loop1-hint, echo = FALSE}
# you are counting the number of "r" or "R". Use an if statement here and update rcount.

```

```{r loop1-solution, echo = FALSE}

rcount <- 0
for (char in chars) {
  if (char == "u" | char == "U") {
    break
  }
  if (char == "r" | char == "R") {
    rcount <- rcount + 1
  }
}

# Print the resulting rcount variable to the console
rcount
```




